MSHS COVID-19 Vaccinations

### 2021-12-10 Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd
Update analysis reference files. Add Peds Dose 2 to Amb Sched Tracking tool.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-11-03.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-11-03.xlsx"),
                           sheet = "Pod Mappings Simple")

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-11-22.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-11-22.xlsx"),
                           sheet = "Pod Mappings Simple")
